---
title: "Homework 04"
---


## TidyTuesday Section (optional)

::: {.callout-important title="Instructions"}

You can count work on this week's TidyTuesday toward the exceptional work required for an A in the Homework component.

:::


Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.
```{r}
library(tidyverse)
```


```{r}
cranes <- read_csv("~/Documents/GitHub/portfolio-my-name-arch/src/tt/cranes.csv")
crane_summary <- cranes %>%
  mutate(observations = as.numeric(observations)) %>%
  filter(comment != 'Record observation') %>%
  group_by(comment) %>%
  summarize(
    avg_observations = mean(observations, na.rm = TRUE),
    .groups = 'drop'
  )


print(crane_summary)


ggplot(crane_summary, aes(x = comment, y = avg_observations, fill = comment)) +

  geom_col(width = 0.6) +
  geom_text(
    # Label the bars with the rounded average value
    aes(label = round(avg_observations, 0)),
    vjust = -0.5, 
    size = 4
  ) +
  labs(
    title = "Average Observations by Comment Type",
    subtitle = "Stat 212 Amin Al Hashim",
    x = "Comment Type",
    y = "Average Number of Observations",
    caption = "Dooley Kim, 10-01-2025, Data source: cranes.csv."
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )
```
The question that I had was is there a relationship between crane observations and the comment on a day. I realized that there are certain comments that are left on days. So I was curious, whether these comments bear any effect on the amount observed. I did not include the record observations because I know that they will obviously have a higher average number of observations.

So what this graph shows me is that the days when there is severe interference or an uncertain amount, we can expect a very high count, but the ends of the season do not see that many observations on average. This makes a bit of sense because logically,because at the borders of the season, it is probably a lot futher from the peak of the season which I would expect to be in the middle of the season. I was a bit surprised at how high severe interference and uncertain amount are.
